Analyzing the influence of Selection on Genetic Programming's Generalization ability in Symbolic Regression

### 2022-06-27 docs/rmd/presentation/slides.Rmd
autogit

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"

@@

* Does the usage of $\epsilon$-lexicase parent selection influence the generalization behavior of genetic programming in symbolic regression if compared to tournament selection?

### Statistical Testing Strategy

1. Differences in average fitness for both algorithms on both datasets?
2. Differences in fitness for training and testing data?

@@

```{r, echo=FALSE, warning=FALSE}
df <- read.csv("../tables/csv/mwu_matrix_error.csv")

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="b"

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="t"

>>>>

```{r vars_dataset echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"

@@

## Hypothesis Testing

**Does the usage of $\epsilon$-lexicase parent selection influence the generalization behavior of genetic programming in symbolic regression if compared to tournament selection?**

1. Test for differences in average fitness between both algorithms
2. Test for differences in average fitness between training and testing data

@@

```{r pvals_fitness, echo=FALSE, warning=FALSE}
df <- read.csv("../tables/csv/mwu_matrix_error.csv")

@@

```{r ea_config, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"

@@

```{r primitive_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="b"

@@

```{r function_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="t"
